ForestClaw: Hybrid forest-of-octrees AMR for hyperbolic conservation laws

### 2013-02-26 docs/parco13/abstract.tex
Tweak for space

\begin{abstract}
%
We present a new hybrid paradigm for parallel adaptive mesh refinement (AMR)
that combines the scalability and lightweight architecture of tree-based AMR
with the computational efficiency of patch-based solvers for hyperbolic
conservation laws.  The key idea is to interpret each leaf of the AMR hierarchy
as one uniform compute patch in $\sR^d$ of dimensions $m^d$, where $m$ is
customarily between 8 and 32.  Thus, computation on each patch can be optimized
for speed, while we inherit the flexibility of adaptive meshes.  In our work we
choose the p4est AMR library as mesh backend since it allows to compose the
mesh from multiple mapped octrees, thus enabling us to work with the cubed
sphere and other nontrivial multiblock geometries.
%
\end{abstract}

\begin{keyword}
adaptive mesh refinement,
clawpack,
HPC,
manycore
\end{keyword}

@@

To enable hardware acceleration for dynamic AMR, we like to build upon the
forest-of-octrees paradigm because of its low overhead and parallel scalability
\cite{BursteddeWilcoxGhattas11}.  We go beyond the traditional high-order
element by introducing a complete compute patch with $m^d$ DOFs as our
macro-element.  In fact, this approach resembles block-structured AMR
\cite{ColellaGravesKeenEtAl07}
% todo cite John B.\ Bell
except that the patches are not overlapping, which enables us to capitalize on
our previous experience with AMR PDE solvers
\cite{BursteddeStadlerAlisicEtAl13}.

>>>>

\begin{abstract}
%
We present a new hybrid paradigm for parallel adaptive mesh refinement (AMR)
that combines the scalability and lightweight architecture of tree-based AMR
with the computational efficiency of patch-based solvers for hyperbolic
conservation laws.  The key idea is to interpret each leaf of the AMR hierarchy
as one uniform compute patch in $\sR^d$ of dimensions $m^d$, where $m$ is
customarily between 8 and 32.  Thus, computation on each patch can be optimized
for speed, while we inherit the flexibility of adaptive meshes.  In our work we
choose to work with the p4est AMR library since it allows to compose the mesh
from multiple mapped octrees, thus enabling the cubed sphere and other
nontrivial multiblock geometries.
%
\end{abstract}

% \begin{keyword}
% adaptive mesh refinement,
% clawpack,
% HPC,
% manycore
% \end{keyword}

@@

To enable hardware acceleration for dynamic AMR, we like to build upon the
forest-of-octrees paradigm because of its low overhead and parallel scalability
\cite{BursteddeWilcoxGhattas11}.  We go beyond the traditional high-order
element by introducing a complete compute patch with $m^d$ DOFs as our
macro-element.  In fact, this approach resembles block-structured AMR
\cite{ColellaGravesKeenEtAl07}
% todo cite John B.\ Bell
except that the patches are not overlapping, which enables us to capitalize on
our previous experience with AMR PDE solvers.
% \cite{BursteddeStadlerAlisicEtAl13}.
